---
title: "Hite Lab Manual v 1.0"
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## GitHub Documents
Welcome and Overview.

Welcome to the lab we are so happy to have you join the team! 

Broadly, research in the lab seeks to advance our understanding of the proximate and evolutionary factors that influence variation in host immune responses and host-pathogen dynamics at the molecular, organismal, and population levels of biological organization.  

To do so, we combine experimental data and functional genetics with mathematical models. This data-theory integration provides a powerful framework for identifying how key mechanisms at the molecular or individual level scale up to influence population-level outcomes. 

We work on a range of host-pathogen systems with a current focus on the genetic model *Drosophila melanogaster* and two gram-negative bacterial pathogens: *Escherichia coli* and *Providencia rettgeri*. To move from the lab to the field, we also have ongoing collaborations with projects involving livestock. The overall goal is to conduct research that advances both basic and applied scientific challenges. 

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
